Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-17 TACAS2018/paper.tex
sec 6.1

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{State observer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In most real implementations, the internal state of a plant cannot be
directly measured but rather inferred from its effect on the output by
using an observer.  Essentially, a state observer is a system that
provides an estimate of the internal state of a given real system,
from measurements of the input and output of the real system.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an observed system}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In this work we are interested in asymptotic stability: asymptotic
stability is a property that amounts to convergence of the model
executions to an equilibrium point, starting from any states in a
neighborhood of the point.

@@

A discrete-time LTI system is
asymptotically stable if all the roots of its characteristic
polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
K$) are inside the unity circle of the complex plane, i.e., their
absolute values are strictly less than one~\cite{astrom1997computer}
(this simple sufficient condition can be generalised, however this is
not necessary in our work).  In this paper, we express this stability
specification $\phi_\mathit{stability}$ in terms of a check known as
\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
formula to select the entries of matrix $K$ so that the closed-loop
dynamics are shaped as desired.

%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally
In this section we assume that
${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization.
%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
For simplicity of the description, we agregate the noises as follows:
$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
A controllable and observable system will have the following dynamics:
\begin{align}
\scriptstyle
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer, and $k_r$ is a reference gain required by the model.

@@

The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
~are called reachability matrices (of the system and its Reachable Canonical Form respectively),
and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.

@@

As stated in Section~\ref{sec:cof_stability}, we use Jury's Criterion on these polynomials
to assert the stability specification.

@@

Thus far we looked at checking stability
%have presented a verification procedure for
of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
$\mathbb{R}$).  The next step we must realize is that the controller and the
observer exist in a digital program, hence their domain is
$\mathbb{R}_{\langle C \rangle}$.  This has two separate effects on the
model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
and the controller are not necessarily those of the plant.  In fact we have
$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{State observer}\label{sec:observer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In most real implementations, the internal state of a plant cannot be
directly measured but rather inferred from its effect on the output by
using an observer.  Essentially, a state observer is a system that
provides an estimate of the internal state of a given real system,
from measurements of the input and output of the real system.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an observed system}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In this work we are interested in asymptotic stability: asymptotic
stability is a property that amounts to convergence of the model
executions to an equilibrium point, starting from any states in a
neighborhood of the point. In the rest of the paper we refer to the
stability specification as $\phi_\mathit{stability}$.

@@

A discrete-time LTI system (as shown in Sec.~\ref{sec:ssrepresentation})
is asymptotically stable if all the roots of its characteristic
polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
K$) are inside the unity circle of the complex plane, i.e., their
absolute values are strictly less than one~\cite{astrom1997computer}
(this simple sufficient condition can be generalised, however this is
not necessary in our work).  We express the stability
specification in terms of a check known as
\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
formula over the coefficients of the characteristic polynomial.
%% to select the entries of matrix $K$ so that the closed-loop
%% dynamics are shaped as desired.

In order to be able to apply Jury's criterion,
in the rest of this section, we compute the  
characteristic polynomial of the observer model.
Note that in this section, we consider that the model is
discretized in the time domain, but not in the value domain.
This essentially means that
${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$, ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d, \mat{L}=\mat{L}_{\langle C \rangle}$ and $\mat{K}=\mat{K}_{\langle C \rangle}$.

%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally

%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
For simplicity of the description, we agregate the noises as follows:
$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
Then, a controllable and observable system will have the following dynamics:
\begin{align}
\scriptstyle
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
%, and $k_r$ is a reference gain required by the model.

@@

The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
~are called reachability matrices (of the system and its reachable canonical form, respectively),
and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.

@@

We get the stability specification by using Jury's Criterion on these polynomials.

@@

While in the previous section, we assumed that
${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization, in this section
we take into consideration the numerical representation and namely the fact that the domain for both
the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.

%% Thus far we looked at checking stability
%% %have presented a verification procedure for
%% of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
%% $\mathbb{R}$).  The next step we must realize is that the controller and the
%% observer exist in a digital program, hence their domain is
%% $\mathbb{R}_{\langle C \rangle}$.

This has two separate effects on the
model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
and the controller are not necessarily those of the plant.  In fact we have
$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.
